Realizing temporal graphs from fastest travel times

### 2023-04-28 TGR Extended - New paper/Realizing TG - extended.tex
NP-hardness picture - new paper

\usetikzlibrary{arrows,decorations.pathmorphing,decorations.pathreplacing,backgrounds,positioning,fit,matrix}
\usetikzlibrary{shapes,calc,patterns,arrows.meta}
\tikzset{
	vert/.style={circle,inner sep=1.5,fill=white,draw,minimum size=.3cm},
	edge/.style={color=black, thick},
	diredge/.style={->,>={Stealth[width=8pt,length=8pt]},color=black, thick},
	timelabel/.style={fill=white,font=\footnotesize, text centered},
	wave/.style={decorate,decoration={coil,aspect=0}},
	dirwave/.style={->, >={Stealth[width=8pt,length=8pt]},decorate,decoration={coil,aspect=0}},
	diredge2/.style={->,>={Stealth[width=8pt,length=8pt]}}
}

@@

	%%Variable X1
	\node (x1t) at (1,0) {};
	\node (x1f) at (3,0) {};

	%%Variable X2
	\node (x2t) at (5,0) {};
	\node (x2f) at (7,0) {};

	%%Variable x3
	\node (x3t) at (9,0) {};
	\node (x3f) at (11,0) {};

	%%Variable x4
	\node (x4t) at (13,0) {};
	\node (x4f) at (15,0) {};

	%% edges among xt, xf vertices
	%x1 to all
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2t);
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3t);
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x2f);
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x3f);
	\draw [dotted,gray] (x1t) [out=30,in=150] to (x4f);

	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2t);
	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3t);
	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x1f) [out=30,in=150] to (x2f);
	\draw [dotted,gray] (x1f) [out=30,in=150] to (x3f);
	\draw [dotted,gray] (x1f) [out=30,in=150] to (x4f);
	%x2 to all
	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3t);
	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x2t) [out=30,in=150] to (x3f);
	\draw [dotted,gray] (x2t) [out=30,in=150] to (x4f);

	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3t);
	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x2f) [out=30,in=150] to (x3f);
	\draw [dotted,gray] (x2f) [out=30,in=150] to (x4f);
	%x3 to all
	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x3t) [out=30,in=150] to (x4f);

	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4t);
	\draw [dotted,gray] (x3f) [out=30,in=150] to (x4f);

	%%Variable X1
	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
	\node[vert,label=above:$x_1$] (x1) at (2,1) {};
	\draw (x1t) -- (x1f) -- (x1) -- (x1t);

	%%Variable X2
	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};
	\draw (x2t) -- (x2f) -- (x2) -- (x2t);

	%%Variable x3
	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};
	\draw (x3t) -- (x3f) -- (x3) -- (x3t);

	%%Variable x4
	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
	\node[vert,label=above:$x_4$] (x4) at (14,1) {};
	\draw (x4t) -- (x4f) -- (x4) -- (x4t);

@@

	%%% edges between x1 gadget and v,c1,c2
	\draw (x1t) to node[timelabel] {$1$} (c1);
	\draw (x1t) to node[timelabel] {$1$} (c2);
	\draw (x1t) to [out=90,in=190] (v);
	\draw (x1f) to [out=90,in=200] node[timelabel] {$3$} (v);

	%%% edges between x2 gadget and v,c1,c2
	\draw (x2f) to node[timelabel] {$1$} (c1);
	\draw (x2t) to node[timelabel] {$1$} (c2);
	\draw (x2t) to [out=80,in=210]  (v);
	\draw (x2f) to node[timelabel] {$3$} (v);

	%%% edges between x3 gadget and v,c1
	\draw (x3t) to node[timelabel] {$1$} (c1);
	\draw (x3t) to node[timelabel] {$3$} (v);
	\draw (x3f) to [out=100,in=330] (v);

	%%% edges between x4 gadget and v,c2
	\draw (x4t) to node[timelabel] {$1$} (c2);
	\draw (x4t) to [out=90,in=340] node[timelabel] {$3$} (v);
	\draw (x4f) to [out=90,in=360] (v);

>>>>

\usetikzlibrary{arrows,decorations.pathmorphing,decorations.pathreplacing,backgrounds,positioning,fit,matrix}
\usetikzlibrary{shapes,calc,patterns,arrows.meta}
\tikzset{
	vert/.style={circle,inner sep=1.5,fill=white,draw=black,minimum size=.3cm},
    dummy/.style={circle,fill=black,draw=black,inner sep=2.5},
	edge/.style={color=black, thick},
	diredge/.style={->,>={Stealth[width=8pt,length=8pt]},color=black, thick},
	timelabel/.style={fill=white,font=\footnotesize, text centered},
	wave/.style={decorate,decoration={coil,aspect=0}},
	dirwave/.style={->, >={Stealth[width=8pt,length=8pt]},decorate,decoration={coil,aspect=0}},
	diredge2/.style={->,>={Stealth[width=8pt,length=8pt]}}
}

@@

	%%Variable X1
	\node[vert,label=left:$x_1^T$] (x1t) at (1,0) {};
	\node[vert,label={[fill=white]right:$x_1^F$}] (x1f) at (3,0) {};
	\node[vert,label=above:$x_1$] (x1) at (2,1) {};

	%%Variable X2
	\node[vert,label={[fill=white]left:$x_2^T$}] (x2t) at (5,0) {};
	\node[vert,label={[fill=white]right:$x_2^F$}] (x2f) at (7,0) {};
	\node[vert,label={[fill=white]above:$x_2$}] (x2) at (6,1) {};

	%%Variable x3
	\node[vert,label={[fill=white]left:$x_3^T$}] (x3t) at (9,0) {};
	\node[vert,label={[fill=white]right:$x_3^F$}] (x3f) at (11,0) {};
	\node[vert,label={[fill=white]above:$x_3$}] (x3) at (10,1) {};

	%%Variable x4
	\node[vert,label={[fill=white]left:$x_4^T$}] (x4t) at (13,0) {};
	\node[vert,label=right:$x_4^F$] (x4f) at (15,0) {};
	\node[vert,label=above:$x_4$] (x4) at (14,1) {};

@@

    %%%%%% EDGES

	%%% edges between x1 gadget and v,c1,c2
    %x1 is TRUE
    %x1 to clause
    \draw (x1t) to node[timelabel] {$3$} (c1);
	\draw (x1t) to node[timelabel,pos=0.25] {$3$} (c2);
    %x1 gadget
    \draw (x1t) to [out=90,in=190] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
	\draw (x1f) to [out=90,in=200] node[dummy] {}
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
    \draw (x1t) to node[timelabel] {$3$} (x1) to node[timelabel] {$1$} (x1f);

	%%% edges between x2 gadget and v,c1,c2
    %x2 is TRUE
    %x2 to clause
	\draw (x2f) to node[timelabel,pos=0.75] {$1$} (c1);
	\draw (x2t) to node[timelabel,pos=0.75] {$1$} (c2);
    %x2 gadget
	\draw (x2t) to [out=80,in=210] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
	\draw (x2f) to node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
    \draw (x2t) to node[timelabel] {$3$} (x2) to node[timelabel] {$1$} (x2f);

    %% edges between x3 gadget and v,c1
    %x3 is FALSE
    %x3 to clause
	\draw (x3t) to node[timelabel,pos=0.75] {$1$} (c1);
    %x3 gadget
	\draw (x3t) to node[timelabel] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
	\draw (x3f) to [out=100,in=330] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
    \draw (x3t) to node[timelabel, pos=0.5] {$1$} (x3) to node[timelabel, pos=0.5] {$3$} (x3f);

    %%% edges between x4 gadget and v,c2
    %x4 is false
    %x4 to clause
	\draw (x4t) to node[timelabel,pos=0.75] {$1$} (c2);
    %x4 gadget
	\draw (x4t) to [out=90,in=340] node[timelabel] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$3$} (v);
	\draw (x4f) to [out=90,in=360] node[dummy] {} 
    node[timelabel,pos=0.25]{$2$} node[pos=0.75,timelabel]{$1$} (v);
    \draw (x4t) to node[timelabel, pos=0.5] {$1$} (x4) to node[timelabel, pos=0.5] {$3$} (x4f);
